%%%%%%%% ICML 2025 SUBMISSION %%%%%%%%%%%%%%%%%

\documentclass{article}

% Recommended packages for figures and better typesetting:
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables
\usepackage{hyperref}
\usepackage{listings}  % For code listings
\usepackage{color}     % For colored text in listings
\usepackage{adjustbox} % For resizing tables to fit column width

% Configure the listings package for source code
\lstset{
  basicstyle=\ttfamily\small,
  breaklines=true,
  commentstyle=\color{gray},
  keywordstyle=\color{blue},
  stringstyle=\color{purple},
  numberstyle=\tiny\color{gray},
  frame=single,
  rulecolor=\color{black},
  backgroundcolor=\color{white},
  tabsize=2,
  captionpos=b
}

% Attempt to make hyperref and algorithmic work together better:
\newcommand{\theHalgorithm}{\arabic{algorithm}}

% Use the following line for the initial blind version submitted for review:
\usepackage[accepted]{icml2025}

\makeatletter
\def\Notice@String{Preliminary work. Under review by the International Conference
on Machine Learning (ICML). Do not distribute.}
\makeatother

% For theorems and such
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{amsthm}
\usepackage[capitalize,noabbrev]{cleveref}

% For drawing diagrams
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows, positioning, fit, backgrounds, matrix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% THEOREMS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{MPF: Aligning via Multi-Perspective Fusion}

\begin{document}

\twocolumn[
\icmltitle{MPF: Aligning and Debiasing Language Models via Post-Training Multi-Perspective Fusion}

% It is OKAY to include author information, even for blind
% submissions: the style file will automatically remove it for you
% unless you've provided the [accepted] option to the icml2025 package.
\icmlsetsymbol{equal}{*}

\begin{icmlauthorlist}
\icmlauthor{Your Name}{equal,aff1}
\icmlauthor{Co-Author}{equal,aff2}
\end{icmlauthorlist}

\icmlaffiliation{aff1}{Your Institution}
\icmlaffiliation{aff2}{Co-Author's Institution}

\icmlcorrespondingauthor{Your Name}{your.email@institution.edu}
\vskip 0.3in
% You may provide any keywords that you find helpful for describing your paper
\icmlkeywords{language models, bias mitigation, ensemble methods, multi-perspective learning, debiasing, model alignment}
]

\begin{abstract}
Multi-Perspective Fusion (MPF) is a novel post-training alignment framework for large language models (LLMs) developed in response to the growing need for easy bias mitigation. Built on top of the SAGED pipeline to interpret bias of LLM, MPF leverages multi-perspective generations to expose and align biases in LLM outputs with nuanced human-like baselines. By decomposing baseline outputs—such as sentiment distributions from HR professionals—into interpretable perspective components, MPF guides generation through sampling and balancing of responses, weighted by the probabilities obtained in the decomposition. Emperically, we evaluate MPF in the context of university and HR's standard, demonstrating its ability to align LLM sentiment distributions with expert baselines and reveal nuanced discorveries. Our results show that MPF offers a scalable and interpretable method for post-hoc alignment and bias mitigation, compatible with existing model architectures and requiring no extensive prompt engineering or fine-tuning.
\end{abstract}

% this must go after the closing bracket ] following \twocolumn[ ...

% This command actually creates the footnote in the first column
% listing the affiliations and the copyright notice.
\printAffiliationsAndNotice{\icmlEqualContribution} % use the standard text.

% Include each section
\input{sections/introduction}
\input{sections/related_work}
\input{sections/methodology}
\input{sections/experiments}
\input{sections/results}
\input{sections/discussion}
\input{sections/conclusion}

\bibliography{references}
\bibliographystyle{icml2025}

\end{document} 